\documentclass{article}
\usepackage[a4paper, landscape, total={260mm, 180mm}]{geometry}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage[T1]{fontenc}

\title{Machine learning-based evidence and attribution mapping of 100,000 climate impact studies - Supplementary material}
\author[1,2]{Max Callaghan}
\author[3,5]{Carl-Friedrich Schleussner}
\author[3,4]{Shruti Nath}
\author[3]{Quentin Lejeune}
\author[6]{Thomas R. Knutson}
\author[7,8]{Markus Reichstein}
\author[]{Gerrit Hansen}
\author[3,5]{Emily Theokritoff}
\author[3,5]{Marina Andrijevic}
\author[3,9]{Robert Brecha}
\author[3]{Michael Hegarty}
\author[3]{Chelsea Jones}
\author[3]{Kaylin Lee}
\author[3]{Agathe Lucas}
\author[3,5]{Nicole van Maanen}
\author[3]{Inga Menke}
\author[3,5]{Peter Pfleiderer}
\author[3]{Burcu Yesil}
\author[1,2]{Jan Minx}




\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
\affil[2]{Priestley International Centre for Climate, University of Leeds, Leeds LS2 9JT, United Kingdom}
\affil[3]{Climate Analytics, Berlin, Germany}
\affil[4]{Institute of Atmospheric and Climate Sciences, ETH Zürich, Switzerland}
\affil[5]{Integrative Research Institute on Transformations of Human-Environment Systems, Humboldt University, Berlin, Germany}
\affil[6]{NOAA/Geophysical Fluid Dynamics Laboratory. Princeton, NJ, 08540, USA}
\affil[7]{Max Planck Institute for Biogeochemistry, Department Biogeochemical Integration, D-07701 Jena, Germany}
\affil[8]{Michael Stifel Center Jena for Data-driven and Simulation Science, Jena, Germany}
\affil[9]{Hanley Sustainability Institute, Renewable and Clean Energy Program and Physics Dept., University of Dayton, Dayton, Ohio, USA}

\date{}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\renewcommand{\arraystretch}{1.5}
\begin{document}
	\maketitle

	\section{Search query}
	\begin{lstlisting}[breaklines,breakatwhitespace=true]
	
	
	(TS=("climate model" OR "elevated* temperatur" OR "ocean* warming" OR "saline* intrusion" OR "chang* climat" OR "environment* change" OR "climat* change" OR "climat* warm" OR "warming* climat" OR "climat* varia" OR "global* warming" OR "global* change" OR "greenhouse* effect" OR "snow cover" OR "extreme temperature" OR "cyclone" OR "ocean acidification" OR "anthropogen*" OR "sea* level" OR "precipitation variabil*" OR "precipitation change*" OR "temperature* impact" OR "environmental* variab" OR "weather* pattern" OR "weather* factor*" OR "climat*") OR TS=("change* NEAR/5 cryosphere" OR "increase* NEAR/3 temperatur*")
	) 
	AND 
	(TS=("migration" OR "impact*" OR "specie*" OR "mortality*" OR "health" OR "disease*" OR "ecosystem*" OR "mass balance" OR "flood*" OR "drought" OR "disease*" OR "adaptation" OR "malaria" OR "fire" OR "water scarcity" OR "water supply" OR "permafrost" OR "biological response" OR "food availability" OR "food security" OR "vegetation dynamic*" OR "cyclone*" OR "yield*" OR "gender" OR "indigenous" OR "conflict" OR "inequality" OR "snow water equival*" OR "surface temp*") OR TS=("glacier* NEAR/3 melt*" OR "glacier* NEAR/3 mass*" OR "erosion* NEAR/5 coast*" OR "glacier* NEAR/5 retreat*" OR "rainfall* NEAR/5 reduc*" OR "coral* NEAR/5 stress*" OR "precip* NEAR/5 *crease*" OR "river NEAR/5 flow")
	) 
	AND 
	(TS=("recent" OR "current" OR "modern" OR "observ*" OR "evidence*" OR "past" OR "local" OR "region*" OR "significant" OR "driver*" OR "driving” OR "respon*" OR "were responsible" OR "was responsible" OR "exhibited" OR "witnessed" OR "attribut*" OR "has increased" OR "has decreased" OR "histor*" OR "correlation" OR "evaluation") 
	)
	
	\end{lstlisting}

	\section{Supplementary Data}
	
	\subsection{Category Scheme}
	The file \textbf{category\_aggregation.csv} lists the categories used to code relevant documents. Each category could be used as an impact or a driver. To make the classification problem tractable, the categories were merged into “broad categories” resembling those used in IPCC AR5. 
	
	\subsection{Document metadata}
	The file \textbf{0c\_doc\_info.csv} contains basic metadata about each of the studies considered. For rights reasons the abstracts are not included, although these are used in the analysis.
	
	\subsection{Predictions}
	
	Predicted scores are given in the following files for relevance \textbf{1\_document\_relevance.csv}, impact category \textbf{1\_impact\_predictions.csv}, and climate drivers \textbf{1\_driver\_predictions.csv}.
	
	\subsection{Grid cells}
	
	The file \textbf{2\_merged\_da\_data.csv} shows the attribution category and weighted studies score (for temperature, precipitation and for all studies) for each grid cell.
	
	\subsection{Study grid cell matching}
	The file \textbf{study\_gridcell\_2.5.csv} has a row for each grid cell study combination, where the column `ndf\_id' refers to the `index' column of the aforementioned grid cell dataset.
	
	\subsection{Study D\&A}
	The file \textbf{2\_study\_da.csv} shows the number of gridcells with each detection and attribution category that each study refers to.
	
	\section{Supplementary Tables}	
	\begin{table}
		\rowcolors{2}{gray!10}{white}
		\scriptsize
		\center
		\input{../tables/continent_sector_n_studies.tex}
		\caption{The number of studies in each impact category and each continent}
	\end{table}

	\begin{table}
		\rowcolors{3}{white}{gray!10}
		\scriptsize
		\center
		\input{../tables/area_pop_sums.tex}
		\caption{The percentage of land area and population with robust evidence by impact category and continent}
	\end{table}

	\begin{table}
		\rowcolors{3}{white}{gray!10}
		\scriptsize
		\center
		\input{../tables/area_pop_sums_income.tex}
		\caption{The percentage of land area and population with robust evidence by impact category and income category}
	\end{table}

	\begin{table}
		\rowcolors{3}{white}{gray!10}
		\scriptsize
		\center
		\input{../tables/area_pop_sums_all.tex}
		\caption{The percentage of land area and population with attributable impacts in temperature and/or precipitation by continent}
	\end{table}
	
	\begin{table}
		\rowcolors{3}{white}{gray!10}
		\scriptsize
		\center
		\input{../tables/area_pop_sums_income_all.tex}
		\caption{The percentage of land area and population with attributable impacts in temperature and/or precipitation by income category}
	\end{table}
	
\end{document}